---
title: "Assignment 5- QMM"
author: "Rohith chandra koyyala"
date: "2022-11-07"
output: word_document
---
### Goal Programming

1. Maximize Z = P - 6C - 3D,
where P = total (discounted) profit over the life of the new products, 
C = change (in either direction) in the current level of employment, 
D = decrease (if any) in next year’s earnings from the current year’s level. 

Since management is primarily focused on attaining some rise to appease the owners, 
the quantity of any gain in earnings does not factor into Z.(It is ambivalent about a significant gain that would be hard to top in coming years.)

The impact of each of the new products (per unit rate of production) on each of these factors is 
shown in the following table: 
  
2)

According on the problem statement, the goal is to:
  
Maximize Z = P - 6*C - 3*D

P = total (discounted) profit over the life of the new products,
C = change (in either direction) in the current level of employment,
D = decrease (if any) in next year’s earnings from the current year’s level.

Subject to:
  
  Total Profit: Maximize P = 20*X1 + 15*X2 + 25*X3

Employment Level: 6*X1 + 4*X2 + 5*X3 = 50

Earnings Next Year: 8*X1 + 7*X2 + 5*X3 >= 75

As a result, the auxillery variables becomes:
  
  Y1 = 6*X1 + 4*X2 + 5*X3 - 50
Y2 = 8*X1 + 7*X2 + 5*X3 - 75

Which means:
  
  (Y1P - Y1M) = 6*X1 + 4*X2 + 5*X3 - 50
(Y2P - Y2M) = 8*X1 + 7*X2 + 5*X3 - 75

Therefore, the final problem statement would be like:
  
  Maximize Z = 20*X1 + 15*X2 + 25*X3 - 6*Y1P - 6*Y1M - 3*Y2M

Subject to the following:
  
  6*X1 + 4*X2 + 5*X3 - (Y1P - Y1M) = 50
8*X1 + 7*X2 + 5*X3 - (Y2P - Y2M) = 75

And:
  
  X1, X2, X3 >= 0
Y1P, Y1M, Y2P, Y2M >= 0

finally, I am going to run linear programming model in R



```{r}
# Here we will require the "lpSolveAPI" library
require(lpSolveAPI)
```


```{r}
# Importing the .lp file for this problem
gp_model <- read.lp("C:/Users/kramr/Downloads/Max.lp")
# Returning the linear programming model
gp_model
```

```{r}
# Solving the linear programming model
solve(gp_model)
# Getting the objectives of linear programming model
get.objective(gp_model)
# Getting the variables of linear programming model
get.variables(gp_model)
```

We can conclude a number of conclusions from the linear programming model's output.

X1 = 0, X2 = 0, X3 = 15, Y1P = 25, Y1M = 0, Y2M = 0, Y2P = 0